The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-07 outputs/docs/events/paper.Rmd
Update paper and some of the meta data around events

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. To reduce the dimensionality of this dataset we then use a topic model that allows correlation and a steady change over time. Finally, we consider the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
  replace_na(list(Parliament = ""))
elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEconomicDates <- read_csv(here::here("inputs/misc/key_dates-economic.csv"), col_types = cols())
keyOtherDates <- read_csv(here::here("inputs/misc/key_dates-other.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())

@@

In this paper we apply a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments and then use a Bayesian hierarchical Dirichlet model to examine events. From a data perspective we contribute **[?????]**. From a methods perspective, we contribute **[?????]**. Our model can be used in many settings where the results of topic models need to be further analysed.

@@

The percentage of stop-words in each record is reasonably consistent over time. This suggests that there is no significant difference in the quality of the parsing over time. Details of this process are provided in Appendix \@ref(stopwordsgraph). We mainly use Hansard records on a daily basis in this paper. Text is usually pre-processed before topic models are used. The specific steps that we take are to remove numbers and punctuation and to change the words to lower case. **[Need to bundle_ngrams i.e. New Zealand is new_zealand.]** Then the sentences are deconstructed and each word considered individually.

@@

```{r exampletopics, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
```

@@

The main output of the STM that is of interest to us is the share of each topic in each document. We would like to know how those shares change given events. But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events. Instead, we use a Bayesian hierarchical Dirichlet model that takes those shares as an input.

We index each proportion, $\gamma$, by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$. Note that time $t$ refers to the day index within a sitting period which is any collection of days separated from other days by at least a week. Our model is:

@@

# Results
We are interested in considering the effect of various events on what is talked about in Australia's parliaments. Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.

Political events are those related to a change of government or an election. Economic events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency. Other events are those such as the 9/11 attacks. The full list of events that we consider are detailed in Appendix \@ref(eventdetails).

We consider four types of events and group the day's topic proportions by these events. One unfortunate effect of this is that we only allow an event to have a long-run effect and ignore short-run effects. Another is that we ignore coincidence of events.

@@

```{r electionsevents, echo=FALSE, fig.cap="Topic proportions grouped by elections", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_election.png"))
```

Figure \@ref(fig:governmentevents) shows the grouping by government. This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election. Similarly, John Howard's three terms are all considered the one government for our purposes.

@@

```{r governmentevents, echo=FALSE, fig.cap="Topic proportions grouped by government", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_government_change.png"))
```

Figure \@ref(fig:economicevents) shows the grouping by major economic changes. There are considerable changes between adjacent events.

```{r economicevents, echo=FALSE, fig.cap="Topic proportions grouped by economic events", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_economic_changes.png"))
```

Figure \@ref(fig:otherevents) shows the grouping by major other events, such as the 9/11 attacks.

```{r otherevents, echo=FALSE, fig.cap="Topic proportions grouped by other events", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/2018-09-28-topics_separated_by_other_changes.png"))
```

Another way to consider the effect of events is by including incrementing variables in the prevelance metadata. This then gets included in the topic modelling and the significance to each topic can be computed. Table \@ref(tab:dodgysignificances) summarises these by the type of dummy and the topic. At the five per cent level the events that we consider were significant for eight topics. This significance tended to be correlated, especially for economic and other events.

```{r dodgysignificances, echo = FALSE, results = 'asis'}

significances %>% 
  kable(booktabs = T, caption = "Significance of dummy") %>%
  kable_styling(font_size = 12)

@@

top_words %>% 
  kable(booktabs = T, caption = "Top words for each topic") %>%
  kable_styling(font_size = 12)

@@

## Hansard sources {#hansardsources}
Where from?

@@

[IS THIS BEING REFERENCED IN THE TEXT????]

@@

```{r economics, echo = FALSE, results = 'asis'}

keyEconomicDates %>% 
  kable(booktabs = T, caption = "Key economic events") %>%
  kable_styling(font_size = 10)

```{r others, echo = FALSE, results = 'asis'}

keyOtherDates %>% 
  kable(booktabs = T, caption = "Key other events") %>%
  kable_styling(font_size = 10)

>>>>

---
output:
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    fig_caption: true
    number_sections: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "The Effect of Events on Australian Parliamentary Discussion (1851--2017)"
thanks: "Thank you to John Tang, Zach Ward, Tim Hatton, Martine Mariotti, Tianyi Wang, Matt Jacob, Leslie Root, Jill Sheppard, Matthew Kerby, Chris Cochrane and Dan Simpson for their helpful suggestions; and to the UC Berkeley Demography Department for the use of their computing resources. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper welcome at: rohan.alexander@anu.edu.au."
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We systematically analyse how parliamentary discussion changes in response to different types of events in Australian history. We first create a dataset of what was said in Australian state and federal parliaments from the mid-1800s through to 2017 based on available public records. To reduce the dimensionality of this dataset we use a topic model that allows for correlation and steady changes over time. We analyse the effect of various events using a Bayesian hierarchical Dirichlet model. We find that: 1) elections are associated with topic changes only when the party in power changes; 2) a change in government can be associated with topic changes even if the party in power does not change; 3) economic events, such as financial crises, have less significant and persistent effects than other events such as terrorist attacks. Our findings have implications for how we think about the longer-term trajectory of government policymaking as the media cycle becomes increasingly focused on short-term events."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
toc: FALSE
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

yearsUsed <- read_csv(here::here("outputs/misc/years_used.csv"), col_types = cols()) %>% 
  replace_na(list(Parliament = ""))
elections <- read_csv(here::here("inputs/misc/misc_elections_data.csv"), col_types = cols())
governments <- read_csv(here::here("inputs/misc/change_of_pm.csv"), col_types = cols())
keyEvents <- read_csv(here::here("inputs/misc/key_events.csv"), col_types = cols())
significances <- read_csv(here::here("outputs/misc/significance.csv"), col_types = cols())
top_words <- read_csv2(here::here("outputs/misc/top_words.csv"), col_types = cols())
missing_days <- read_csv(here::here("outputs/misc/missing_days.csv"), col_types = cols())
hansard_sources <- read_csv(here::here("outputs/misc/hansard_sources.csv"), col_types = cols())

@@

In this paper we apply a topic model to a dataset of larger-scale parliamentary text records from multiple Australian parliaments and then use a Bayesian hierarchical Dirichlet model to examine events. From a data perspective we contribute **[TBD]**. From a methods perspective, we contribute **[TBD]**. Our model can be used in many settings where the results of topic models need to be further analysed.

@@

The percentage of stop-words in each record is reasonably consistent over time. This suggests that there is no significant difference in the quality of the parsing over time. Details of this process are provided in Appendix \@ref(stopwordsgraph). We mainly use Hansard records on a daily basis in this paper. Text is usually pre-processed before topic models are used. The specific steps that we take are to remove numbers and punctuation and to change the words to lower case. **[Need to bundle_ngrams i.e. New Zealand is new_zealand and ad valorem is ad_valorem.]** Then the sentences are deconstructed and each word considered individually.

@@

```{r exampletopics, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/topics_example.pdf"))
```

@@

The main output of the STM that is of interest to us is the proportion of each topic in each document. We would like to know how those proportions change given events. But with around 80 **[UPDATE]** topics for each of the roughly 54,331 **[UPDATE]** sitting days across the parliaments and houses the data are still too noisy to easily visualise changes around events. Instead, we use a Bayesian hierarchical Dirichlet model that takes those proportions as an input.

We index each proportion, $\gamma$, by sitting period $s$, time $t$ and topic $p$, that is $\gamma_{stp}$. For this purpose time, $t$, refers to the day index within a sitting period, and a sitting period is any collection of days separated from another collection of days by at least a week. Our model is:

@@

# Results
We are interested in considering the effect of various events on what is talked about in Australia's parliaments. 
<!-- Each of the parliaments and their houses are treated independently here. Future work could expand the model to better understand, and allow, for correlation between them.  -->
Political events are those related to a change of government or an election. Other events are defined by substantial changes in various economic measures, such as the onset of the Great Depression or floating the currency; events of a historical magnitude, such as entering into a war or the 9/11 attacks; or events that had a significant effect on Australian life, such as hosting the Olympics, or the Mabo decision. The full list of events that we consider are detailed in Appendix \@ref(eventdetails).

First considering the mean topic distributions over governments, Figures \@ref(fig:mu1to20) - \@ref(fig:mu41to60).

```{r mu1to20, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/mu_topic1-20.pdf"))
```

```{r mu21to40, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/mu_topic21-40.pdf"))
```

```{r mu41to60, cache = TRUE, echo=FALSE, fig.cap="Illustrative topic model output, with Topic 17 highlighted", out.width = '100%'}
knitr::include_graphics(here::here("outputs/figures/mu_topic41-60.pdf"))
```

Topics related to Federation such as the British Empire and the constitution decrease in importance over time. A substantial increase in the importance of issues dealing with

Increasing from 20th gov: 2, 4, 8, 12,

32 increases and then decreases

Increases only recently: 33, 35

Breakpoint: 23, 25, 49, 48, 46, 47, 41

@@

Groupings by government. This can be different to election groupings, for instance, the change from the Rudd to Gillard governments happened without an election. Similarly, John Howard's three terms are all considered the one government for our purposes.

@@

@@

top_words %>% 
  kable(booktabs = T, caption = "Top words for each topic") %>%
  kable_styling(font_size = 8)

@@

## Hansard sources {#hansardsources}

Hansard records are available from a variety of sources, as detailed in Table \ref{tab:hansardsourcestable}.

```{r hansardsourcestable, cache = TRUE, echo = FALSE, results = 'asis'}

hansard_sources %>%
  kable(
    booktabs = T,
    align = c('l', 'r', 'r', 'r'),
    caption = "Hansard sources and notes") %>%
  kable_styling(font_size = 10)

# Break cachee

Detail where from, and which years are being used and why.

@@

@@

```{r keyevents, echo = FALSE, results = 'asis'}

keyEvents %>% 
  kable(booktabs = T, caption = "Key events") %>%
  kable_styling(font_size = 10)
